%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Jonathan T Moshier
\documentclass[margin,line]{resume}
\usepackage{hyperref, soul, marvosym}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\so{\Large Jonathan Moshier}}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    location: denver, co, usa   \hfill website: jonmoshier.com\vspace{0mm}\\\vspace{0mm}%
    telephone: 1 (303) 859-2569 \hfill linkedin: linkedin.com/in/jmoshier\vspace{0mm}\\\vspace{0mm}%
    email: jonmoshier@gmail.com \hfill github: github.com/jonmoshier\vspace{0mm}\\\vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Objective}
 To work with smart, dedicated people, solving challenging problems and building great things. I'm at home on fast moving teams using agile processes with quick iterations. I'm happiest in entrepreneurial roles where I'm involved in the bigger picture.
 %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming Skills} 
	Generalist, self taught, full stack developer. I have a diversified background working with C\# and .net in the healthcare space as well as Python and Linux work. I'm frequently evaluating new technology, most recently I've taken an interest in cryptocurrency as well as Scala and Rust. I bring a background in Economics and a concern for the end user to everything I work on.
	%__________________________________________________________________________________________________________________
% Professional Experience
\section{\mysidestyle Professional Experience - Software}

    \textbf{Transmed Systems}, Washington, D.C \vspace{1mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{August 2010 -- present}\vspace{1mm}\\\vspace{0mm}%
	Was brought on as the 6\textsuperscript{th} employee of this now 22 employee private company. I came on as a junior .net engineer, working with everything from company infrastructure to user facing products. Our primary product is a browser based BioInformatics platform, that allows clinicians to analyze hospital data.
\vspace{-3mm}\\\vspace{1mm}
    \begin{list2}
    \item Lead architect, developer \& project owner for our applications data importer. Allows users to import Excel spreadsheets into our applications database for analysis. This tool uses Silverlight, C\#, and MS SQL.
    \item Lead architect, developer \& project owner of an audit logging and reporting system using log4net, ASP.net, C\#, and logparser, an existing tool that allows flat files to be queried using SQL statements.
    \item System Administration using CentOS to develop an analytics package using R/Rserve, tested the analysis tools package using Amazon's AWS as well as in-house servers before deploying to customer sites.
  \end{list2}
Worked on various "nuts-and-bolts" jobs, including:
\begin{list2}
    \item Switching our company wide email to Google apps.
    \item Building our continuous deployment process using TFS and MSBuild.
    \item Stress testing our application using 3\textsuperscript{rd} party tools.
  \end{list2}
	
 \section{\mysidestyle Professional Experience - Non-Software}
   
 \textbf{The Kitchen Cafe}, Boulder, Colorado, USA \vspace{1mm}\\\vspace{1mm}%
    \textsl{Line Chef} \hfill \textbf{February 2009 -- July 2010} \vspace{-3mm}\\\vspace{-1mm}%
	\begin{list2}
	\item Worked all stations in this two kitchen, two dining room restaurant
	\item Ran the [Upstairs] kitchen and menu two nights a week providing excellent casual food for a Lounge/Bar restaurant setting
	\end{list2}

    \textbf{FreeWave Technologies}, Boulder, Colorado, USA \vspace{1mm}\\\vspace{1mm}%
    \textsl{Customer Support Technician and Inside Sales Representative} \hfill \textbf{April 2006 -- December 2006} \vspace{-3mm}\\\vspace{-1mm}%
	\begin{list2}
	\item Worked with customers via phone, email and in person to help understand radio application and configuration
	\item Lead Export Management Group to ensure compliance with all U.S. Export Laws
	\end{list2}

     %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of California Santa Cruz Extension}, Santa Clara, California, USA \vspace{1mm}\\\vspace{1mm}%
    \textsl{Extracurricular learning in} \hfill \textbf{September 2010 - March 2011}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item C\# Programming for the .Net Framework
        \item Molecular Biology	
    \end{list2}\vspace{-1.5mm}

\textbf{University of Colorado Boulder}, Boulder, Colorado, USA \vspace{1mm}\\\vspace{1mm}%
    \textsl{Bachelors of Science, Economics} \hfill \textbf{ August 2009}\vspace{-3mm}\\\vspace{-1mm}%


%__________________________________________________________________________________________________________________
% Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}

%______________________________________________________________________________________________________________________
% EOF

